Notes on Perturbational Quantities

### 2008-10-24 docs/pert_notes/pert.tex
addressed the marginpar about the psi forcing in the (rho h)_0 equation.  now the code includes it, and the document reflects this.

\subsection{Predicting $(\rho h)'$ ({\tt enthalpy\_pred\_type = 1} - default)}
Due to operator splitting, the call to {\tt react\_state} has already
been made.  Hence, the goal is to compute an edge state enthalpy
starting from $(\rho h)^{(1)}$ using an enthalpy equation that does
not include the $\rho H_{\rm nuc}$ and $\rho H_{\rm ext}$ terms, where
were already accounted for in {\tt react\_state}
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \dot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\MarginPar{Does $\psi$ need to be included in the force?  I have
written it in the base state equation for now, even though neither the
base state or perturbational edge state prediction in the code uses
$\psi$.  How about evolving density first, then computing a
time-centered $\psi$ to be used as the energy forcing?}
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}}_{"(\rho h)_0 ~ \text{force}"}
+ \psi.\label{rhoh0 equation}
\end{eqnarray}
Subtracting (\ref{rhoh0 equation}) from (\ref{rhoh equation}) and rearranging terms gives 
the perturbational enthalpy equation
\begin{eqnarray}
\frac{\partial(\rho h)'}{\partial t} &=& -\nabla\cdot[(\rho h)'\Ub] 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} 
+ \nabla\cdot\kth\nabla T\nonumber \\
&=& -\Ub\cdot\nabla(\rho h)' \underbrace{- (\rho h)'\nabla\cdot\Ub 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r}
+ \nabla\cdot\kth\nabla T}_{"(\rho h)' ~ \text{force}"}. \label{rhohprime equation}
\end{eqnarray}

>>>>

\subsection{Predicting $(\rho h)'$ ({\tt enthalpy\_pred\_type = 1} - default)}
Due to operator splitting, the call to {\tt react\_state} has already
been made.  Hence, the goal is to compute an edge state enthalpy
starting from $(\rho h)^{(1)}$ using an enthalpy equation that does
not include the $\rho H_{\rm nuc}$ and $\rho H_{\rm ext}$ terms, where
were already accounted for in {\tt react\_state}
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{"(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}
Subtracting (\ref{rhoh0 equation}) from (\ref{rhoh equation}) and rearranging terms gives 
the perturbational enthalpy equation
\begin{eqnarray}
\frac{\partial(\rho h)'}{\partial t} &=& -\nabla\cdot[(\rho h)'\Ub] 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r} 
+ \nabla\cdot\kth\nabla T\nonumber \\
&=& -\Ub\cdot\nabla(\rho h)' \underbrace{- (\rho h)'\nabla\cdot\Ub 
- \nabla\cdot[(\rho h)_0\Ubt] + (\Ubt \cdot \er)\frac{\partial p_0}{\partial r}
+ \nabla\cdot\kth\nabla T}_{"(\rho h)' ~ \text{force}"}. \label{rhohprime equation}
\end{eqnarray}
